---
title: "502 Project EDA"
author: "Madeline Chang"
output:
 pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(dplyr)
library(forcats)
library(ggplot2)
library(rpart)
library(caret)
library(rpart.plot)
library(C50)
library(Metrics)
library(e1071)
library(glmnet)
```

Reading in data

```{r}
recruitment<- read.csv('/Users/mtc/ADS/ADS 502/Project/recruitment_data.csv')

recruitment<- recruitment %>%
  mutate(Gender = as.factor(Gender),
         EducationLevel = as.factor(EducationLevel),
         RecruitmentStrategy = as.factor(RecruitmentStrategy),
         HiringDecision = as.factor(HiringDecision),
         Gender_name = as.factor(ifelse(Gender == 0, "Male", "Female")),
         Hiring_name = as.factor(ifelse(HiringDecision == 0, "Not Hired", "Hired")),
         Recruitment_name = fct_collapse(RecruitmentStrategy,
                                        Aggressive = 1,
                                        Moderate = 2,
                                        Conservative = 3),
         Education_name = fct_collapse(EducationLevel,
                                       Bachelor_1 = 1,
                                       Bachelor_2 = 2,
                                       Masters = 3,
                                       PhD = 4))
```

Data Quality

```{r}
colSums(is.na(recruitment))
```

```{r}
near_zero<- nearZeroVar(recruitment) # no columns with zero or near-zero variance

corr<- cor(recruitment[,c(1, 4, 5, 6, 7, 8, 9)])
high_corr <- findCorrelation(corr, cutoff = 0.75) # no numeric columns with high correlation with each other
```


Distribution of Variables

```{r}
hist<- function(col, bin_num){
  ggplot(data = recruitment) +
    geom_histogram(aes(x = .data[[col]]), bins = bin_num) +
    xlab(col)
}


hist("Age", 20)

hist("ExperienceYears", 15) +
  xlab("Years of Experience")

hist("PreviousCompanies", 5) +
  xlab("Number of Previous Companies")

hist("DistanceFromCompany", 30) +
  xlab("Distance from Company")

hist("InterviewScore", 25) +
  xlab("Interview Score")

hist("SkillScore", 25)+
  xlab("Skill Score")

hist("PersonalityScore", 25) +
  xlab("Personality Score")
```

```{r}
bar<- function(col){
  ggplot(data = recruitment) +
    geom_bar(aes(x = .data[[col]])) +
    xlab(col)
}

bar("Gender_name") +
  xlab("Sex")

bar("Education_name") +
  xlab("Education Type")

bar("Recruitment_name") +
  xlab("Recruitment Level")

bar("Hiring_name") +
  xlab("Hiring Outcome")
```

```{r}
ggplot(data = recruitment) +
  geom_bar(aes(x = Recruitment_name, fill = Hiring_name)) +
  xlab("Recruitment Type") +
  guides(fill = guide_legend(title = "Hiring Decision"))

ggplot(data = recruitment) +
  geom_bar(aes(x = Gender_name, fill = Hiring_name)) +
  xlab("Sex of Applicant") +
  guides(fill = guide_legend(title = "Hiring Decision"))

ggplot(data = recruitment) +
  geom_bar(aes(x = Education_name, fill = Hiring_name)) +
  xlab("Education Level") +
  guides(fill = guide_legend(title = "Hiring Decision"))
```

```{r}
hiring_point<- function(x, y){
  ggplot(data = recruitment) +
    geom_point(aes(x = .data[[x]], y = .data[[y]], color = Hiring_name))
}

hiring_point("SkillScore", "PersonalityScore") + 
  guides(color = guide_legend(title = "Hiring Decision"))

hiring_point("SkillScore", "InterviewScore") +
  guides(color = guide_legend(title = "Hiring Decision"))
```


```{r}
ggplot(data = recruitment) +
  geom_point(aes(x = SkillScore, y = InterviewScore, color = Gender_name))+
  facet_grid(~Hiring_name) + 
  guides(color = guide_legend(title = "Sex of Applicant"))

ggplot(data = recruitment) +
  geom_point(aes(x = SkillScore, y = PersonalityScore, color = Gender_name)) +
  facet_grid(~Hiring_name) + 
  guides(color = guide_legend(title = "Sex of Applicant"))
```

```{r}
set.seed(720)

trainingRows <- createDataPartition(recruitment$Hiring_name, p = .75, list = FALSE) 

recruit_train <- recruitment[trainingRows, ]
recruit_test <- recruitment[-trainingRows, ]
```

```{r}
log_reg<- glm(HiringDecision ~ Age + Gender + EducationLevel + ExperienceYears + PreviousCompanies + DistanceFromCompany + InterviewScore + SkillScore + PersonalityScore + RecruitmentStrategy, data = recruit_train, family = "binomial")

summary(log_reg)

exp(log_reg$coefficients)
```

Combine both bachelors degrees into one level- not statistically significant
No need for age or gender (seen in EDA and logistic model), previous companies and distance are not statistically significant.

What seems to be most important are aggressive recruiting strategy and education at masters level or above. (See exponentiated coefficients from logistic regression model)

